The \project{unRAVE} catalog

### 2016-08-18 article/unrave.tex
Some framework text about globular clusters

Assembling a training set for the main-sequence and sub-giant branch was not as
straightforward.
% training set from K2/EPIC?!!

% Identifying obviously bad stars that have been mis-classified by K2/EPIC

@@

\subsection{External validation}

@@

\subsection{Astrophysical validation}
% Astrophysical validation:
% --> Identify globular clusters and look to see whether we capture "expected" abundance trends/spreads that are seen elsewhere in the literature
% --> Residuals as a function of galactic position? (DIBS)

@@

\begin{thebibliography}{dummy}
\bibitem[Astropy Collaboration et 
al.(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, Astronomy \& Astrophysics, 558, AA33

@@

@@

>>>>

Assembling a training set for the main-sequence and sub-giant branch was more complex.
% training set from K2/EPIC?!!
% Identifying obviously bad stars that have been mis-classified by K2/EPIC

% Magic wizardry for missing and imperfect labels.

@@

\subsection{External validation}
\label{sec:external-validation}

@@

\subsection{Astrophysical validation}

After verifying that our stellar labels are comparable with other
high-resolution studies, here we verify that the abundance labels we find
are consistent with expectations from astrophysics.  One example is stars in
globular clusters, which show anti-correlations in light element abundances 
\citep[e.g.,][and references therein]{Da_Costa,Carretta_2009}.  In the \rave\
survey we found 70 stars with positions and radial velocities that are
consistent with being members of globular clusters.  Specifically we identified
49 stars belonging to NGC~5139 ($\omega$~Centauri), 11 members of the retrograde
globular cluster NGC~3201, and 10 members of NGC~362.  
% TODO: Were any of these stars unintentionally in the training set?
All of these systems are well-studied and exhibit abundance anti-correlations 
in Na--O and Mg--Al \citep{people}.  Other correlations are also present 
(e.g., C--N), but those relationships are less relevant for this work because 
we do not measure C and N abundances here.

We show the detailed abundances for these globular cluster members in
Figure \ref{fig:globular-cluster-abundances}.  For comparison purposes we
have included abundances from the high-resolution studies of \citep{people}.
\stub{What do we find?}

% Assuming we recover these relationships...
Indeed, this demonstrates that our abundance labels can be used to identify
globular cluster members that are now tidally disrupted \citep{Anguiano_2016,Kuzma_2016,Navin_2016},
even for stars with low S/N ratios.

% Some literature notes:
% See http://iopscience.iop.org/article/10.1088/0004-637X/731/1/64/pdf
% NGC 3201 has Na-O anti-correlation: Carretta et al. (2009)
% NGC 362 has "two discrete groups along the Na-O anti-correlation": https://arxiv.org/abs/1307.4085
% NGC 362 has Mg-Al relationship (low Mg scatter, large Al scatter) --> Carretta (2013)
% NGC 3201 has Mg-Al relationship (http://arxiv.org/pdf/1305.3645.pdf and references therein)

% Astrophysical validation:
% --> Residuals as a function of galactic position? (DIBS)

@@

\begin{thebibliography}{dummy}

\bibitem[Anguiano et al.(2016)]{Anguiano_2016} Anguiano, B., De Silva, G.~M., Freeman, K., et al.\ 2016, \mnras, 457, 2078

\bibitem[Astropy Collaboration et 
al.(2013)]{astropy} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, Astronomy \& Astrophysics, 558, AA33

@@

\bibitem[Kuzma et al.(2016)]{Kuzma_2016} Kuzma, P.~B., Da Costa, G.~S., Mackey, A.~D., \& Roderick, T.~A.\ 2016, \mnras, 461, 3639

@@

\bibitem[Navin et al.(2016)]{Navin_2016} Navin, C.~A., Martell, S.~L., \& Zucker, D.~B.\ 2016, arXiv:1606.06430
